---
title: "Feature selection on PNC"
author: "FMJ Bulot (florentin.bulot@centraliens.net)"
date: "Last generated: `r format(Sys.time(), '%d %B, %Y, %H:%M')`"
output:
  html_document:
    df_print: paged
    code_folding: hide
    toc: true
    toc_depth: 2
    toc_float:
      collapsed: false
knit: (function(inputFile, encoding) { 
      out_dir <- '../docs';
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file=file.path(dirname(inputFile), out_dir, 'feature_selection_pnc.html'))})
editor_options: 
  markdown: 
    wrap: 80
---



```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='../docs/figs/feature_selection_pnc/',warning=FALSE, message=FALSE)
```

This notebook explores the impact of the following factors on the readings of
the PMS5003:

-   RH

-   number of UFP

-   number of particles below 0.8um

-   number of particles above 0.8um

-   total particle number

-   source of PM

This is done only on peak concentration, with all the data from each experiment.
Aggregating the results per experiment yield data sets that are too small to be 
meaningful.

The target is the PNC reported by the sensors.

This is done using different feature selection algorithms:
- Boruta
- Ridge 
- recursive feature selection with  SVM




# Data preparation

```{r}


source("variables.r")
source("utilities.r")
require(Boruta)
require(lubridate)

df_sensors <- readRDS(sensors_file) %>%
  get_sensor_type()
df_ops <- readRDS(ops_file_transformed)
df_nanotracer <- readRDS(nanotracer_file)


df_sensors_ft <- df_sensors %>%
  ungroup() %>%
  group_by(date, variation, source, exp, sensor_type) %>%
  summarise(across(where(is.numeric), ~ mean(., na.rm = T)))


df_nanotracer$date <- round_date(df_nanotracer$date, unit = "10 s")
df_nanotracer_ft <- df_nanotracer %>%
  dplyr::select(date, N.1.)

df_ops_ft <- df_ops %>%
  mutate(
    lw08um = Bin.1 + Bin.2 + Bin.3 + Bin.4 + Bin.5 + Bin.6 * (0.8 - 0.721) /
      (0.897 - 0.721),
    gr08um = Bin.6 * (0.897 - 0.8) / (0.897 - 0.721) + Bin.7 + Bin.8 + Bin.9 + Bin.10 + Bin.11 + Bin.12 + Bin.13 + Bin.14 + Bin.15 + Bin.16 + Bin.17,
    total_particle_number = Bin.1 + Bin.2 + Bin.3 + Bin.4 + Bin.5 + Bin.6 + Bin.7 + Bin.8 + Bin.9 + Bin.10 + Bin.11 + Bin.12 + Bin.13 + Bin.14 + Bin.15 + Bin.16 + Bin.17
  ) %>%
  dplyr::select(-variation,-exp,-source)


df_joined <- df_sensors_ft %>%
  ungroup() %>%
  inner_join(df_ops_ft, by = c("date")) %>%
  inner_join(df_nanotracer_ft, by = c("date"))

head(df_joined)

df_joined_ft <- df_joined %>%
  #dplyr::filter(exp != "") %>%
  dplyr::filter(variation == "Peaks") %>%
  mutate(rh = ifelse(grepl("54%", exp), 54,
                     ifelse(
                       grepl("69%", exp), 69,
                       ifelse(grepl("72%", exp), 72,
                              ifelse(grepl("76%", exp), 76, 79))
                     )),
         source = ifelse(source == "Incense", 1, 0))


df_joined_ft <- df_joined_ft %>%
  rename(
    Bin.1_0.3um = Bin.1,
    Bin.2_0.374um = Bin.2,
    Bin.3_0.465um = Bin.3,
    Bin.4_0.579um = Bin.4,
    Bin.5_0.721um = Bin.5,
    Bin.6_0.897um = Bin.6,
    Bin.7_1.117um = Bin.7,
    Bin.8_1.391um = Bin.8,
    Bin.9_1.732um = Bin.9,
    Bin.10_2.156um = Bin.10,
    Bin.11_2.685um = Bin.11,
    Bin.12_3.343um = Bin.12,
    Bin.13_4.162um = Bin.13,
    Bin.14_5.182um = Bin.14,
    Bin.15_6.451um = Bin.15,
    Bin.16_8.031um = Bin.16,
    Bin.17_10um = Bin.17
  )



frmla <-
  gr03um  ~  source + lw08um + N.1. + total_particle_number + rh


#frmla <- bias ~  source + lw08um + N.1. + total_particle_number + rh
#frmla_inter <- bias ~  (source + lw08um + N.1. + total_particle_number + rh )^2

require(caret)
trControl <- trainControl(
  method = "repeatedcv",
  number = 10,
  search = "grid",
  repeats = 10
)

require(doParallel)
no_cores <- parallel::detectCores() - 1
cluster <- makePSOCKcluster(no_cores)
registerDoParallel(cluster)



```



# Feature selection



## Boruta {.tabset}



### PMS5003 {.tabset}

#### gr03um {.tabset}

```{r}




frmla <- gr03um  ~  source + lw08um + N.1. + total_particle_number + rh

boruta_output <-
  Boruta(
    frmla,
    data = dplyr::filter(df_joined_ft, sensor_type == "PMS5003"),
    doTrace = 0
  )

boruta_output

roughFixMod <- TentativeRoughFix(boruta_output)
boruta_signif <- getSelectedAttributes(roughFixMod)
print(boruta_signif)

imps <- attStats(roughFixMod)
imps2 = imps[imps$decision != 'Rejected', c('meanImp', 'decision')]
head(imps2[order(-imps2$meanImp),])

plot(
  boruta_output,
  cex.axis = .7,
  las = 2,
  xlab = "",
  main = "Variable Importance - gr03um"
)  
```


#### gr05um {.tabset}

```{r}

frmla <- gr05um  ~  source + lw08um + N.1. + total_particle_number + rh

boruta_output <-
  Boruta(
    frmla,
    data = dplyr::filter(df_joined_ft, sensor_type == "PMS5003"),
    doTrace = 0
  )

boruta_output

roughFixMod <- TentativeRoughFix(boruta_output)
boruta_signif <- getSelectedAttributes(roughFixMod)
print(boruta_signif)

imps <- attStats(roughFixMod)
imps2 = imps[imps$decision != 'Rejected', c('meanImp', 'decision')]
head(imps2[order(-imps2$meanImp),])

plot(
  boruta_output,
  cex.axis = .7,
  las = 2,
  xlab = "",
  main = "Variable Importance -  gr05um"
)  
```


#### gr10um {.tabset}

```{r}



frmla <- gr10um  ~  source + lw08um + N.1. + total_particle_number + rh

boruta_output <-
  Boruta(
    frmla,
    data = dplyr::filter(df_joined_ft, sensor_type == "PMS5003"),
    doTrace = 0
  )

boruta_output

roughFixMod <- TentativeRoughFix(boruta_output)
boruta_signif <- getSelectedAttributes(roughFixMod)
print(boruta_signif)

imps <- attStats(roughFixMod)
imps2 = imps[imps$decision != 'Rejected', c('meanImp', 'decision')]
head(imps2[order(-imps2$meanImp),])

plot(
  boruta_output,
  cex.axis = .7,
  las = 2,
  xlab = "",
  main = "Variable Importance - gr10um"
)  
```

#### gr25um {.tabset}

```{r}




frmla <- gr25um  ~  source + lw08um + N.1. + total_particle_number + rh

boruta_output <-
  Boruta(
    frmla,
    data = dplyr::filter(df_joined_ft, sensor_type == "PMS5003"),
    doTrace = 0
  )

boruta_output

roughFixMod <- TentativeRoughFix(boruta_output)
boruta_signif <- getSelectedAttributes(roughFixMod)
print(boruta_signif)

imps <- attStats(roughFixMod)
imps2 = imps[imps$decision != 'Rejected', c('meanImp', 'decision')]
head(imps2[order(-imps2$meanImp),])

plot(
  boruta_output,
  cex.axis = .7,
  las = 2,
  xlab = "",
  main = "Variable Importance - gr25um"
)  
```



### SPS30 {.tabset}

#### n05 {.tabset}

```{r}



frmla <- n05  ~  source + lw08um + N.1. + total_particle_number + rh

boruta_output <-
  Boruta(
    frmla,
    data = dplyr::filter(df_joined_ft, sensor_type == "SPS030"),
    doTrace = 0
  )

boruta_output

roughFixMod <- TentativeRoughFix(boruta_output)
boruta_signif <- getSelectedAttributes(roughFixMod)
print(boruta_signif)

imps <- attStats(roughFixMod)
imps2 = imps[imps$decision != 'Rejected', c('meanImp', 'decision')]
head(imps2[order(-imps2$meanImp),])

plot(
  boruta_output,
  cex.axis = .7,
  las = 2,
  xlab = "",
  main = "Variable Importance - n05"
)  
```

#### n1 {.tabset}

```{r}



frmla <- n1  ~  source + lw08um + N.1. + total_particle_number + rh

boruta_output <-
  Boruta(
    frmla,
    data = dplyr::filter(df_joined_ft, sensor_type == "SPS030"),
    doTrace = 0
  )

boruta_output

roughFixMod <- TentativeRoughFix(boruta_output)
boruta_signif <- getSelectedAttributes(roughFixMod)
print(boruta_signif)

imps <- attStats(roughFixMod)
imps2 = imps[imps$decision != 'Rejected', c('meanImp', 'decision')]
head(imps2[order(-imps2$meanImp),])

plot(
  boruta_output,
  cex.axis = .7,
  las = 2,
  xlab = "",
  main = "Variable Importance - n1"
)  
```


#### n25 {.tabset}

```{r}


frmla <- n25  ~  source + lw08um + N.1. + total_particle_number + rh

boruta_output <-
  Boruta(
    frmla,
    data = dplyr::filter(df_joined_ft, sensor_type == "SPS030"),
    doTrace = 0
  )

boruta_output

roughFixMod <- TentativeRoughFix(boruta_output)
boruta_signif <- getSelectedAttributes(roughFixMod)
print(boruta_signif)

imps <- attStats(roughFixMod)
imps2 = imps[imps$decision != 'Rejected', c('meanImp', 'decision')]
head(imps2[order(-imps2$meanImp),])

plot(
  boruta_output,
  cex.axis = .7,
  las = 2,
  xlab = "",
  main = "Variable Importance - n25"
)  
```


### OPCR1 {.tabset}

#### Bin0 - 0.35/0.7um 

```{r}



frmla <-
  Bin0  ~  source + lw08um + N.1. + total_particle_number + rh

boruta_output <-
  Boruta(
    frmla,
    data = dplyr::filter(df_joined_ft, sensor_type == "OPCR1"),
    doTrace = 0
  )

boruta_output

roughFixMod <- TentativeRoughFix(boruta_output)
boruta_signif <- getSelectedAttributes(roughFixMod)
print(boruta_signif)

imps <- attStats(roughFixMod)
imps2 = imps[imps$decision != 'Rejected', c('meanImp', 'decision')]
head(imps2[order(-imps2$meanImp),])

plot(
  boruta_output,
  cex.axis = .7,
  las = 2,
  xlab = "",
  main = "Variable Importance -  bin0"
)  
```

#### Bin1 - 0.7/1.1um {.tabset}

```{r}



frmla <-
  Bin1  ~  source + lw08um + N.1. + total_particle_number + rh

boruta_output <-
  Boruta(
    frmla,
    data = dplyr::filter(df_joined_ft, sensor_type == "OPCR1"),
    doTrace = 0
  )

boruta_output

roughFixMod <- TentativeRoughFix(boruta_output)
boruta_signif <- getSelectedAttributes(roughFixMod)
print(boruta_signif)

imps <- attStats(roughFixMod)
imps2 = imps[imps$decision != 'Rejected', c('meanImp', 'decision')]
head(imps2[order(-imps2$meanImp),])

plot(
  boruta_output,
  cex.axis = .7,
  las = 2,
  xlab = "",
  main = "Variable Importance -  bin1"
)  
```

#### Bin2 - 1.1/1.5um {.tabset}

```{r}



frmla <-
  Bin2  ~  source + lw08um + N.1. + total_particle_number + rh

boruta_output <-
  Boruta(
    frmla,
    data = dplyr::filter(df_joined_ft, sensor_type == "OPCR1"),
    doTrace = 0
  )

boruta_output

roughFixMod <- TentativeRoughFix(boruta_output)
boruta_signif <- getSelectedAttributes(roughFixMod)
print(boruta_signif)

imps <- attStats(roughFixMod)
imps2 = imps[imps$decision != 'Rejected', c('meanImp', 'decision')]
head(imps2[order(-imps2$meanImp),])

plot(
  boruta_output,
  cex.axis = .7,
  las = 2,
  xlab = "",
  main = "Variable Importance -  bin2"
)  
```

#### Bin3 - 1.5/1.9um {.tabset}

```{r}



frmla <-
  Bin3  ~  source + lw08um + N.1. + total_particle_number + rh

boruta_output <-
  Boruta(
    frmla,
    data = dplyr::filter(df_joined_ft, sensor_type == "OPCR1"),
    doTrace = 0
  )

boruta_output

roughFixMod <- TentativeRoughFix(boruta_output)
boruta_signif <- getSelectedAttributes(roughFixMod)
print(boruta_signif)

imps <- attStats(roughFixMod)
imps2 = imps[imps$decision != 'Rejected', c('meanImp', 'decision')]
head(imps2[order(-imps2$meanImp),])

plot(
  boruta_output,
  cex.axis = .7,
  las = 2,
  xlab = "",
  main = "Variable Importance -  bin3"
)  
```

#### Bin4 - 1.9/2.4um {.tabset}

```{r}



frmla <-
  Bin4  ~  source + lw08um + N.1. + total_particle_number + rh

boruta_output <-
  Boruta(
    frmla,
    data = dplyr::filter(df_joined_ft, sensor_type == "OPCR1"),
    doTrace = 0
  )

boruta_output

roughFixMod <- TentativeRoughFix(boruta_output)
boruta_signif <- getSelectedAttributes(roughFixMod)
print(boruta_signif)

imps <- attStats(roughFixMod)
imps2 = imps[imps$decision != 'Rejected', c('meanImp', 'decision')]
head(imps2[order(-imps2$meanImp),])

plot(
  boruta_output,
  cex.axis = .7,
  las = 2,
  xlab = "",
  main = "Variable Importance -  bin4"
)  
```






## Recursive feature elimination - SVM {.tabset}


### PMS5003 {.tabset}

#### gr03um {.tabset}

```{r}



frmla <-
  gr03um  ~  source + lw08um + N.1. + total_particle_number + rh


subsets <- c(1:6)
x <- df_joined_ft %>%
  dplyr::filter(sensor_type == "PMS5003") %>%
  dplyr::select(source, lw08um, total_particle_number, rh, N.1., gr03um)


svmProfile <- rfe(
  gr03um ~ .,
  data = x,
  sizes = c(1:6),
  rfeControl = rfeControl(
    functions = caretFuncs,
    number = 10,
    method = "repeatedcv"
  ),
  ## pass options to train()
  method = "svmRadial"
)



svmProfile


predictors(svmProfile)

varImp(svmProfile)


data.frame(Overall = svmProfile$variables$Overall,
           var = svmProfile$variables$var) %>%
  group_by(var) %>%
  summarise(mean(Overall, na.rm = T))

```



#### gr05um {.tabset}

```{r}




frmla <-
  gr05um  ~  source + lw08um + N.1. + total_particle_number + rh

x <- df_joined_ft %>%
  dplyr::filter(sensor_type == "PMS5003") %>%
  dplyr::select(source, lw08um, total_particle_number, rh, N.1., gr05um)

svmProfile <- rfe(
  gr05um ~ .,
  data = x,
  sizes = c(1:6),
  rfeControl = rfeControl(
    functions = caretFuncs,
    number = 10,
    method = "repeatedcv"
  ),
  ## pass options to train()
  method = "svmRadial"
)



svmProfile


predictors(svmProfile)

varImp(svmProfile)


data.frame(Overall = svmProfile$variables$Overall,
           var = svmProfile$variables$var) %>%
  group_by(var) %>%
  summarise(mean(Overall, na.rm = T))
```


#### gr10um {.tabset}

```{r}


frmla <- gr10um  ~  source + lw08um + N.1. + total_particle_number + rh 

x <- df_joined_ft %>%
  dplyr::filter(sensor_type == "PMS5003") %>%
  dplyr::select(source, lw08um, total_particle_number, rh, N.1.,gr10um)

svmProfile <- rfe(gr10um~., data = x,
                  sizes = c(1:6),
                  rfeControl = rfeControl(functions = caretFuncs,
                                          number = 10,
                                          method = "repeatedcv"),
                  ## pass options to train()
                  method = "svmRadial")



svmProfile


predictors(svmProfile)

varImp(svmProfile)


data.frame(Overall = svmProfile$variables$Overall, var = svmProfile$variables$var) %>%
  group_by(var) %>%
  summarise(mean(Overall, na.rm=T))

```

#### gr25um {.tabset}

```{r}



frmla <- gr25um  ~  source + lw08um + N.1. + total_particle_number + rh 

x <- df_joined_ft %>%
  dplyr::filter(sensor_type == "PMS5003") %>%
  dplyr::select(source, lw08um, total_particle_number, rh, N.1.,gr25um)

svmProfile <- rfe(gr25um~., data = x,
                  sizes = c(1:6),
                  rfeControl = rfeControl(functions = caretFuncs,
                                          number = 10,
                                          method = "repeatedcv"),
                  ## pass options to train()
                  method = "svmRadial")



svmProfile


predictors(svmProfile)

varImp(svmProfile)


data.frame(Overall = svmProfile$variables$Overall, var = svmProfile$variables$var) %>%
  group_by(var) %>%
  summarise(mean(Overall, na.rm=T))
```



### SPS30 {.tabset}

#### n05 {.tabset}

```{r}


frmla <- n05  ~  source + lw08um + N.1. + total_particle_number + rh 

subsets <- c(1:6)
x <- df_joined_ft %>%
  dplyr::filter(sensor_type == "SPS030") %>%
  dplyr::select(source, lw08um, total_particle_number, rh, N.1., n05)

svmProfile <- rfe(n05~., data = x,
                  sizes = c(1:6),
                  rfeControl = rfeControl(functions = caretFuncs,
                                          number = 10,
                                          method = "repeatedcv"),
                  ## pass options to train()
                  method = "svmRadial")



svmProfile


predictors(svmProfile)

varImp(svmProfile)


data.frame(Overall = svmProfile$variables$Overall, var = svmProfile$variables$var) %>%
  group_by(var) %>%
  summarise(mean(Overall, na.rm=T))

```

#### n1 {.tabset}

```{r}


frmla <- n1  ~  source + lw08um + N.1. + total_particle_number + rh 
x <- df_joined_ft %>%
  dplyr::filter(sensor_type == "SPS030") %>%
  dplyr::select(source, lw08um, total_particle_number, rh, N.1., n1)

svmProfile <- rfe(n1~., data = x,
                  sizes = c(1:6),
                  rfeControl = rfeControl(functions = caretFuncs,
                                          number = 10,
                                          method = "repeatedcv"),
                  ## pass options to train()
                  method = "svmRadial")



svmProfile


predictors(svmProfile)

varImp(svmProfile)


data.frame(Overall = svmProfile$variables$Overall, var = svmProfile$variables$var) %>%
  group_by(var) %>%
  summarise(mean(Overall, na.rm=T))
```


#### n25 {.tabset}

```{r}


frmla <- n25  ~  source + lw08um + N.1. + total_particle_number + rh 

x <- df_joined_ft %>%
  dplyr::filter(sensor_type == "SPS030") %>%
  dplyr::select(source, lw08um, total_particle_number, rh, N.1., n25)

svmProfile <- rfe(n25~., data = x,
                  sizes = c(1:6),
                  rfeControl = rfeControl(functions = caretFuncs,
                                          number = 10,
                                          method = "repeatedcv"),
                  ## pass options to train()
                  method = "svmRadial")



svmProfile


predictors(svmProfile)

varImp(svmProfile)


data.frame(Overall = svmProfile$variables$Overall, var = svmProfile$variables$var) %>%
  group_by(var) %>%
  summarise(mean(Overall, na.rm=T))

```


### OPCR1 {.tabset}

#### Bin0 - 0.35/0.7um 

```{r}


frmla <- Bin0  ~  source + lw08um + N.1. + total_particle_number + rh 



subsets <- c(1:6)
x <- df_joined_ft %>%
  dplyr::filter(sensor_type == "OPCR1") %>%
  dplyr::select(source, lw08um, total_particle_number, rh, N.1., Bin0)

svmProfile <- rfe(Bin0~., data = x,
                  sizes = c(1:6),
                  rfeControl = rfeControl(functions = caretFuncs,
                                          number = 10,
                                          method = "repeatedcv"),
                  ## pass options to train()
                  method = "svmRadial")



svmProfile


predictors(svmProfile)

varImp(svmProfile)


data.frame(Overall = svmProfile$variables$Overall, var = svmProfile$variables$var) %>%
  group_by(var) %>%
  summarise(mean(Overall, na.rm=T))

```

#### Bin1 - 0.7/1.1um {.tabset}

```{r}


frmla <- Bin1  ~  source + lw08um + N.1. + total_particle_number + rh 


x <- df_joined_ft %>%
  dplyr::filter(sensor_type == "OPCR1") %>%
  dplyr::select(source, lw08um, total_particle_number, rh, N.1., Bin1)

svmProfile <- rfe(Bin1~., data = x,
                  sizes = c(1:6),
                  rfeControl = rfeControl(functions = caretFuncs,
                                          number = 10,
                                          method = "repeatedcv"),
                  ## pass options to train()
                  method = "svmRadial")



svmProfile


predictors(svmProfile)

varImp(svmProfile)


data.frame(Overall = svmProfile$variables$Overall, var = svmProfile$variables$var) %>%
  group_by(var) %>%
  summarise(mean(Overall, na.rm=T))

```

#### Bin2 - 1.1/1.5um {.tabset}

```{r}


frmla <- Bin2  ~  source + lw08um + N.1. + total_particle_number + rh 

x <- df_joined_ft %>%
  dplyr::filter(sensor_type == "OPCR1") %>%
  dplyr::select(source, lw08um, total_particle_number, rh, N.1., Bin2)

svmProfile <- rfe(Bin2~., data = x,
                  sizes = c(1:6),
                  rfeControl = rfeControl(functions = caretFuncs,
                                          number = 10,
                                          method = "repeatedcv"),
                  ## pass options to train()
                  method = "svmRadial")



svmProfile


predictors(svmProfile)

varImp(svmProfile)


data.frame(Overall = svmProfile$variables$Overall, var = svmProfile$variables$var) %>%
  group_by(var) %>%
  summarise(mean(Overall, na.rm=T))

```

#### Bin3 - 1.5/1.9um {.tabset}

```{r}


frmla <- Bin3  ~  source + lw08um + N.1. + total_particle_number + rh 

x <- df_joined_ft %>%
  dplyr::filter(sensor_type == "OPCR1") %>%
  dplyr::select(source, lw08um, total_particle_number, rh, N.1., Bin3)

svmProfile <- rfe(Bin3~., data = x,
                  sizes = c(1:6),
                  rfeControl = rfeControl(functions = caretFuncs,
                                          number = 10,
                                          method = "repeatedcv"),
                  ## pass options to train()
                  method = "svmRadial")



svmProfile


predictors(svmProfile)

varImp(svmProfile)


data.frame(Overall = svmProfile$variables$Overall, var = svmProfile$variables$var) %>%
  group_by(var) %>%
  summarise(mean(Overall, na.rm=T))
```

#### Bin4 - 1.9/2.4um {.tabset}

```{r}


frmla <- Bin4  ~  source + lw08um + N.1. + total_particle_number + rh 

x <- df_joined_ft %>%
  dplyr::filter(sensor_type == "OPCR1") %>%
  dplyr::select(source, lw08um, total_particle_number, rh, N.1., Bin4)

svmProfile <- rfe(Bin4~., data = x,
                  sizes = c(1:6),
                  rfeControl = rfeControl(functions = caretFuncs,
                                          number = 10,
                                          method = "repeatedcv"),
                  ## pass options to train()
                  method = "svmRadial")



svmProfile


predictors(svmProfile)

varImp(svmProfile)


data.frame(Overall = svmProfile$variables$Overall, var = svmProfile$variables$var) %>%
  group_by(var) %>%
  summarise(mean(Overall, na.rm=T))

```









## Ridge {.tabset}


### PMS5003 {.tabset}

#### gr03um {.tabset}

```{r}


frmla <- gr03um  ~  source + lw08um + N.1. + total_particle_number + rh 

trControl <- trainControl(method = "repeatedcv",
    number = 10,
    search = "grid",
    repeats = 10)

tuneGrid <- expand.grid(alpha = 0,
                        lambda = seq(0.0001, 1, length = 100))


glmnet.fit <- train(frmla, data = df_joined_ft[df_joined_ft$sensor_type == "PMS5003", ], 
                method = "glmnet", metric = "RMSE",
                preProcess = c("center", "scale"),
                trControl = trControl,
                tuneGrid = tuneGrid)

glmnet.fit$bestTune
varImp(glmnet.fit)
```


#### gr05um {.tabset}

```{r}



frmla <- gr05um  ~  source + lw08um + N.1. + total_particle_number + rh 

glmnet.fit <- train(frmla, data = df_joined_ft[df_joined_ft$sensor_type == "PMS5003", ], 
                method = "glmnet", metric = "RMSE",
                preProcess = c("center", "scale"),
                trControl = trControl,
                tuneGrid = tuneGrid)

glmnet.fit$bestTune
varImp(glmnet.fit)
```


#### gr10um {.tabset}

```{r}


frmla <- gr10um  ~  source + lw08um + N.1. + total_particle_number + rh 

glmnet.fit <- train(frmla, data = df_joined_ft[df_joined_ft$sensor_type == "PMS5003", ], 
                method = "glmnet", metric = "RMSE",
                preProcess = c("center", "scale"),
                trControl = trControl,
                tuneGrid = tuneGrid)

glmnet.fit$bestTune
varImp(glmnet.fit)
```

#### gr25um {.tabset}

```{r}



frmla <- gr25um  ~  source + lw08um + N.1. + total_particle_number + rh 

glmnet.fit <- train(frmla, data = df_joined_ft[df_joined_ft$sensor_type == "PMS5003", ], 
                method = "glmnet", metric = "RMSE",
                preProcess = c("center", "scale"),
                trControl = trControl,
                tuneGrid = tuneGrid)

glmnet.fit$bestTune
varImp(glmnet.fit)
```



### SPS30 {.tabset}

#### n05 {.tabset}

```{r}


frmla <- n05  ~  source + lw08um + N.1. + total_particle_number + rh 

glmnet.fit <- train(frmla, data = df_joined_ft[df_joined_ft$sensor_type == "SPS030", ], 
                method = "glmnet", metric = "RMSE",
                preProcess = c("center", "scale"),
                trControl = trControl,
                tuneGrid = tuneGrid)

glmnet.fit$bestTune
varImp(glmnet.fit)
```

#### n1 {.tabset}

```{r}


frmla <- n1  ~  source + lw08um + N.1. + total_particle_number + rh 

glmnet.fit <- train(frmla, data = df_joined_ft[df_joined_ft$sensor_type == "SPS030", ], 
                method = "glmnet", metric = "RMSE",
                preProcess = c("center", "scale"),
                trControl = trControl,
                tuneGrid = tuneGrid)

glmnet.fit$bestTune
varImp(glmnet.fit)
```


#### n25 {.tabset}

```{r}


frmla <- n25  ~  source + lw08um + N.1. + total_particle_number + rh 

glmnet.fit <- train(frmla, data = df_joined_ft[df_joined_ft$sensor_type == "SPS030", ], 
                method = "glmnet", metric = "RMSE",
                preProcess = c("center", "scale"),
                trControl = trControl,
                tuneGrid = tuneGrid)

glmnet.fit$bestTune
varImp(glmnet.fit)
```


### OPCR1 {.tabset}

#### Bin0 - 0.35/0.7um 

```{r}


frmla <- Bin0  ~  source + lw08um + N.1. + total_particle_number + rh 

glmnet.fit <- train(frmla, data = df_joined_ft[df_joined_ft$sensor_type == "OPCR1", ], 
                method = "glmnet", metric = "RMSE",
                preProcess = c("center", "scale"),
                trControl = trControl,
                tuneGrid = tuneGrid)

glmnet.fit$bestTune
varImp(glmnet.fit)
```

#### Bin1 - 0.7/1.1um {.tabset}

```{r}


frmla <- Bin1  ~  source + lw08um + N.1. + total_particle_number + rh 


glmnet.fit <- train(frmla, data = df_joined_ft[df_joined_ft$sensor_type == "OPCR1", ], 
                method = "glmnet", metric = "RMSE",
                preProcess = c("center", "scale"),
                trControl = trControl,
                tuneGrid = tuneGrid)

glmnet.fit$bestTune
varImp(glmnet.fit)
```

#### Bin2 - 1.1/1.5um {.tabset}

```{r}


frmla <- Bin2  ~  source + lw08um + N.1. + total_particle_number + rh 


glmnet.fit <- train(frmla, data = df_joined_ft[df_joined_ft$sensor_type == "OPCR1", ], 
                method = "glmnet", metric = "RMSE",
                preProcess = c("center", "scale"),
                trControl = trControl,
                tuneGrid = tuneGrid)

glmnet.fit$bestTune
varImp(glmnet.fit)
```

#### Bin3 - 1.5/1.9um {.tabset}

```{r}


frmla <- Bin3  ~  source + lw08um + N.1. + total_particle_number + rh 


glmnet.fit <- train(frmla, data = df_joined_ft[df_joined_ft$sensor_type == "OPCR1", ], 
                method = "glmnet", metric = "RMSE",
                preProcess = c("center", "scale"),
                trControl = trControl,
                tuneGrid = tuneGrid)

glmnet.fit$bestTune
varImp(glmnet.fit)
```

#### Bin4 - 1.9/2.4um {.tabset}

```{r}


frmla <- Bin4  ~  source + lw08um + N.1. + total_particle_number + rh 


glmnet.fit <- train(frmla, data = df_joined_ft[df_joined_ft$sensor_type == "OPCR1", ], 
                method = "glmnet", metric = "RMSE",
                preProcess = c("center", "scale"),
                trControl = trControl,
                tuneGrid = tuneGrid)

glmnet.fit$bestTune
varImp(glmnet.fit)
```
